Lab2

### 2021-07-26 notebooks/DataCleaning.Rmd

```{r import libraries}
library(tidyverse)
library(ggplot2) 
library(sandwich)
library(stargazer)

@@

d_covid <- read.csv(file = './JAL_Lab2/src/data/covid-counties.csv')
d_openings <- read.csv(file = './JAL_Lab2/src/data/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './JAL_Lab2/src/data/Trips_by_Distance_-_2020.csv')
```

>>>>

```{r import libraries}
library(tidyverse)
library(ggplot2) 
library(sandwich)
library(stargazer)
library(plyr)
library(dplyr)

@@

d_covid <- read.csv(file = './../src/data/covid-counties.csv')
d_openings <- read.csv(file = './../src/data/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../src/data/Trips_by_Distance_-_2020.csv')
```

```{r filter data}
#filter by date, month of april, 2020
d_covid <- filter(d_covid, date >= "2020-04-01", date <= "2020-04-30")
d_trips <- filter(d_trips, Date >= "4/1/2020", Date <= "4/30/2020")

#sum values for each county
covid_col <- ddply(d_covid, "county", numcolwise(sum))
trips_col <- ddply(d_trips, "County.Name", numcolwise(sum))

#clean county name format
d_trips$county <- gsub("([A-Za-z]+).*", "\\1", d_trips$County.Name)
trips_col$county <- gsub("([A-Za-z]+).*", "\\1", trips_col$County.Name)

#code to merge state info to d
d <- merge(x = trips_col, y = covid_col, by = "county")
d <- merge(x = d, y = d_trips[ , c("county", "State.Postal.Code")], by = "county", all.x=TRUE)

#merge county policies to d
d_openings$strict <- d_openings$Closed.bars.x2 != "0"

d_openings$State.Postal.Code <- d_openings$State.Abbreviation
d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)

#drop na and duplicates
d <- d %>% drop_na()
d <- unique(d)
```
